\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-19 Manuscript/manuscript.tex
tasks for owen to update the analysis with gamlss

\subsection{GLMM} \label{subsec:Results_GLMM}

>>>>

\subsection{GAMLSS} \label{subsec:Results_GLMM}

\jy{Owen, please prepare the following:
1) A table of the model parameter estimates (both point estimate and
standard error). This is similar to the current table, with and
without 2022 data. Let's focus on model gg3b and leave the model
comparison results in the supplement.
2) Figure: random effects at the venue level with/without 2022
data. Similar to the current figure.
3) Diagnostic plots: qq-plot for the gg3b model. QQ-plot for the
normal random effects could be placed in supplement.
4) Table: assessing the 0.1 threshold, similar to the current table.
I'll take care of the writing when you get the results.}
